SDR enhancement by clouds

### 2024-03-27 article/article.Rmd
Commit 2024-03-27 11:12

There are some propositions of the underling mechanism of those events as summarized
by @Gueymard2017, and include scattering on the edge of cumulus clouds or through
thin cirrus.  Further investigation with radiation transfer modeling methods and
observations have pointed as the prevailing explanation, the forward Mie scattering
[@Pecenak2016; @Thuillier2013; @Yordanov2013; @Yordanov2015].
The overall phenomenon can depend on different interactive factors, that include cloud
thickness and constitution, and the relative position of the sun, the clouds and the observer.
As such, th

@@

<!-- our work -->
In this study, we used modeled clear sky irradiance, in order to identify cloud
enhancement. We studied their occurrences, intensity and duration, in a thirty year
period at the city of Thessaloniki. We were able to determine some trends of the
phenomenon, it's Climatology, and some other statistical characteristics.

>>>>

There are some propositions of the underling mechanism of those events as summarized
by @Gueymard2017, and include scattering on the edge of cumulus clouds or through
thin cirrus.  Further investigation with radiation transfer modeling methods and
observations have pointed as the prevailing explanation, the forward Mie scattering
[@Pecenak2016; @Thuillier2013; @Yordanov2013; @Yordanov2015].
The overall phenomenon depends on different interactive factors, that include cloud
thickness and constitution, and the relative position of the sun, the clouds and the
observer.  As such, there can be multiple contributing mechanism that create the
observed enhancements.

@@

<!-- our work -->
In this study, we used modeled clear sky irradiance, in order to identify cloud
enhancement. We studied their occurrences, intensity and duration, in a thirty year
period at the city of Thessaloniki. We were able to determine some trends of the
phenomenon, it's Climatology, and some of its general characteristics.

### 2024-03-27 article/article.tex
Commit 2024-03-27 11:12

\title{SDR enhancement by clouds}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{A Short Subtitle}
\author{Athanasios N. Natsis\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:abais@auth.gr}{\nolinkurl{abais@auth.gr}}}} \and Charikleia Meleti\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:meleti@auth.gr}{\nolinkurl{meleti@auth.gr}}}}}
\date{2024-03-26}

@@

The underling mechanism of those events have been studied, with the main factor to be
\ldots. cite \ldots{}
The forward scattering of clouds near the sun has been observed to produce cases of
extreme enhancement irradiances (Yordanov, Saetre, and Midtgård 2015).

@@

In this study, we used modeled clear sky irradiance, in order to identify cloud
enhancement. We studied their occurrences, intensity and duration, in a thirty year
period at the city of Thessaloniki. We were able to determine some trends of the
phenomenon, it's Climatology, and some other statistical characteristics.

In the relative bibliography different definition have been used for these events, some of
the are summarized by (\textbf{Gueymard2017?}).
Here, we defined as cloud enhancement events (CE) the cases when the measured
global horizontal irradiance (GHI) at ground level, exceeds the expected value under
clear-sky conditions.
Similar, we defined as extreme cloud enhancement events (ECE), the cases when GHI,
exceeds the Total Solar Irradiance on horizontal plane at ground level.
Although the duration of these bursts varies, from instantaneous to several minutes,
here we are constrained by the recorded data, to one-minute steps.

@@

@@

@@

@@

>>>>

\title{SDR enhancement by clouds}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{A Short Subtitle}
\author{Athanasios N. Natsis\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:abais@auth.gr}{\nolinkurl{abais@auth.gr}}}} \and Charikleia Meleti\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:meleti@auth.gr}{\nolinkurl{meleti@auth.gr}}}}}
\date{2024-03-27}

@@

There are some propositions of the underling mechanism of those events as summarized
by Gueymard (2017), and include scattering on the edge of cumulus clouds or through
thin cirrus. Further investigation with radiation transfer modeling methods and
observations have pointed as the prevailing explanation, the forward Mie scattering
(Pecenak et al. 2016; Thuillier et al. 2013; G. H. Yordanov et al. 2013; Georgi Hristov Yordanov, Saetre, and Midtgård 2015).
The overall phenomenon depends on different interactive factors, that include cloud
thickness and constitution, and the relative position of the sun, the clouds and the
observer. As such, there can be multiple contributing mechanism that create the
observed enhancements.

The forward scattering of clouds near the sun has been observed to produce cases of
extreme enhancement irradiances (Georgi Hristov Yordanov, Saetre, and Midtgård 2015).

@@

In this study, we used modeled clear sky irradiance, in order to identify cloud
enhancement. We studied their occurrences, intensity and duration, in a thirty year
period at the city of Thessaloniki. We were able to determine some trends of the
phenomenon, it's Climatology, and some of its general characteristics.

In the relative bibliography different definition have been used for these events, some of
the are summarized by Gueymard (2017).
Here, we defined as cloud enhancement events (CE) the cases when the measured
global horizontal irradiance (GHI) at ground level, exceeds the expected value under
clear-sky conditions.
Similar, we defined as extreme cloud enhancement events (ECE), the cases when GHI,
exceeds the Total Solar Irradiance on horizontal plane at ground level.
Although the duration of these bursts varies, from instantaneous to several minutes,
here we are constrained by the recorded data, to one-minute steps.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Gueymard2017}{}}%
Gueymard, Christian A. 2017. {``Cloud and Albedo Enhancement Impacts on Solar Irradiance Using High-Frequency Measurements from Thermopile and Photodiode Radiometers. Part 1: Impacts on Global Horizontal Irradiance.''} \emph{Solar Energy} 153: 755--65. \url{https://doi.org/gb283c}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Pecenak2016}{}}%
Pecenak, Zachary K., Felipe A. Mejia, Ben Kurtz, Amato Evan, and Jan Kleissl. 2016. {``Simulating Irradiance Enhancement Dependence on Cloud Optical Depth and Solar Zenith Angle.''} \emph{Solar Energy} 136 (October): 675--81. \url{https://doi.org/10.1016/j.solener.2016.07.045}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Thuillier2013}{}}%
Thuillier, Gérard, Jean-Marie Perrin, Philippe Keckhut, and François Huppert. 2013. {``Local Enhanced Solar Irradiance on the Ground Generated by Cirrus: Measurements and Interpretation.''} \emph{Journal of Applied Remote Sensing} 7 (1): 073543. \url{https://doi.org/10.1117/1.JRS.7.073543}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Yordanov2013}{}}%
Yordanov, G. H., O.-M. Midtgård, T. O. Saetre, H. K. Nielsen, and L. E. Norum. 2013. {``Overirradiance (Cloud Enhancement) Events at High Latitudes.''} \emph{{IEEE} Journal of Photovoltaics} 3 (1): 271--77. \url{https://doi.org/10.1109/JPHOTOV.2012.2213581}.
